---
output:
  html_document:
    self_contained: yes
    highlight: null
    mathjax: null
    theme: default
    code_folding : hide
    toc : true
    number_sections : true
params:
  startDate : '2020-08-26'
  endDate : '2020-08-27'
  tableName   : '`vaca_ta`'
  calltime_aca: 'callstarttime'
  calltime_ecl: 'calltime'
  programID : 'bskybinternal'
  queue : 'platform'
  vaca_filter : "and customgroup = 'platform classic'"
  eval_filter : "and area like '%platform%'"
  cg_filter : " callgroup like '%balerion%' and iscurrent = 1"
  fileName : "Negative_Gain_Report"
  bucket : 5
  database : "bskybsatmap"
  CG_calls_filter : 10
  optimizationmetric : ['issavedtv', 'issavedtv_trueup']
  user : 'satmap_ai_bskyb'
  pass : "$bskyb#123"
  host : '10.105.2.57'
  port : 3307
  top : 0.7
  NormalisationFactor : floor(cp_actual*10)
---
---
  title: `r paste0('Negative Gain Report for ', params$queue)`
---
  
```{r packages, include=FALSE , warning=FALSE , message=FALSE}
library(DBI)
library(dplyr)
library(tidyr)
library(ggplot2)
library(RMySQL)
library(data.table)
library(stringr)
#library(modelr)
library(scales)
library(knitr)
library(kableExtra)
library(lubridate)
library(RColorBrewer)
library(plotly)
library(shiny)
# cols <- rev(brewer.pal(11, 'RdYlBu'))
```


```{r rounding, echo=FALSE , warning=FALSE , message=FALSE}
round_off <- function(df){
  x <- df %>%
    mutate_if(is.numeric, round, digits=3)
  return(x)
}
```


```{r vacaQuery , include=FALSE , echo=FALSE , warning=FALSE , message=FALSE}

vacaQuery <- function(params){
  
  optims <- params$optimizationmetric
  
  for(i in 1:length(optims)){
    optims[i] <- paste0(optims[i], " as optimizationmetric_", i)
  }
  
  optims <- paste0(optims, collapse = ",")
  my_query = paste0("SELECT callGuid, " , params$calltime_aca , " as ct ,", optims, ", nagent , on_off 
                    FROM " , params$tableName , "
                    where " , params$calltime_aca , " between '" , params$startDate , "' and '" , params$endDate  ,"' and
                    " , params$calltime_ecl , " between '" , params$startDate , "' and '" , params$endDate  ,"' and isRelevant = 1 ",params$vaca_filter,";
                    ")
  return(my_query)
}

```


```{r cgQuery , include=FALSE , echo=FALSE , warning=FALSE , message=FALSE}

cgQuery <- function(params){
  
  my_query = paste0("select * from ",params$database,".`", params$programID , "_platform.callGroups`
                    where   ",params$cg_filter,";
                    ")
  return(my_query)
}

```

```{r evalLogQuery , include=FALSE , echo=FALSE , warning=FALSE , message=FALSE}

evalLogQuery <- function(params){
  
  my_query = paste0("SELECT * ,  ", params$NormalisationFactor ," as nf
                    FROM ",params$database,".`bskybinternal.vevaluatorlog`
                    where callTime between '" , params$startDate , "' and '" , params$endDate  ,"' ",params$eval_filter,";
                    ")
  return(my_query)
}
```

```{r get_vaca , include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

my_query <- vacaQuery(params)

MySQLConnect216AI <- dbConnect(dbDriver("MySQL"),user=params$user, password=params$pass,
                               dbname=params$database, host=params$host, port = params$port)


VARNAME <- dbGetQuery(MySQLConnect216AI, my_query); 

on.exit(dbDisconnect(MySQLConnect216AI))

dist=as.data.frame(VARNAME)

all_cons <- dbListConnections(MySQL())
#print(all_cons)
for(con in all_cons)
  +  dbDisconnect(con)
print(paste(length(all_cons), " connections killed."))

vaca = dist
setnames(vaca, tolower(names(vaca)))
```


```{r get_CG, include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

my_query <- cgQuery(params)

MySQLConnect216AI <- dbConnect(dbDriver("MySQL"),user=params$user, password=params$pass,
                               dbname=params$database, host=params$host, port = params$port)


VARNAME <- dbGetQuery(MySQLConnect216AI, my_query); 

on.exit(dbDisconnect(MySQLConnect216AI))

dist=as.data.frame(VARNAME)

all_cons <- dbListConnections(MySQL())
#print(all_cons)
for(con in all_cons)
  +  dbDisconnect(con)
print(paste(length(all_cons), " connections killed."))
cg = dist
cg <- cg %>%
  arrange(CP_MixPercentile)
rn <- 1:length(cg[,1])
cg <- cbind(cg,rn)
setnames(cg, tolower(names(cg)))

```


```{r get_evalLog, include=FALSE, echo=FALSE  , warning=FALSE , message=FALSE}

my_query <- evalLogQuery(params)

MySQLConnect216AI <- dbConnect(dbDriver("MySQL"),user=params$user, password=params$pass,
                               dbname=params$database, host=params$host, port = params$port)


VARNAME <- dbGetQuery(MySQLConnect216AI, my_query); 

on.exit(dbDisconnect(MySQLConnect216AI))

dist=as.data.frame(VARNAME)

all_cons <- dbListConnections(MySQL())
#print(all_cons)
for(con in all_cons)
  +  dbDisconnect(con)
print(paste(length(all_cons), " connections killed."))
evalLog = dist
setnames(evalLog, tolower(names(evalLog)))
```


```{r Joins, warning= FALSE , echo= FALSE , message= FALSE}
vaca_cols <- colnames(vaca)[grep("optimization",colnames(vaca))]
vaca_eval_cols <- c("callguid",'on_off' = 'on_off.x','skill' = 'skill','calltime'='ct', 'ap_actual' , 'cp_actual' ,  'callguid','ap_loggedinpercentile','callgroup','nf' , 'evalscore_raw' , 'nagent', vaca_cols)
vacaEval <- vaca %>%
  left_join(evalLog , by = 'callguid') %>%
  select(vaca_eval_cols) 

vacaEval <- vacaEval[!is.na(vacaEval$ap_actual),]

vacaEval <- vacaEval[!is.na(vacaEval$cp_actual),]
vacaEval <- vacaEval %>%
  filter(cp_actual < 1)
vacaEval$nagent <- as.numeric(vacaEval$nagent)

```



```{r L3D, echo=F , warning=FALSE , message=FALSE}
kable(sprintf('%s and %s' ,params$startDate , params$endDate)) %>% kable_styling()

```


```{r gain_summary, warning= FALSE , echo= FALSE , message= FALSE}
gain_summary <- function(opt_metric)
{
  setDT(vacaEval)
  vacaEval <- copy(vacaEval)
  setnames(vacaEval, opt_metric, "opt_metric")

  vacaEval[, date := as.Date(calltime)]
  vacaEval[, ap_q := as.integer(floor(ap_actual*10) + 1)]
  vacaEval[, cp_q := as.integer(floor(cp_actual*10) + 1)]
  
  res1 <- vacaEval[,.(calls = .N, sales = sum(opt_metric), cr = mean(opt_metric)), by = .(date = as.character(date), on_off = ifelse(on_off == 0, "OFF", "ON"))]
  res2 <- vacaEval[,.(calls = .N, sales = sum(opt_metric), cr = mean(opt_metric)), by = .(date = as.character(date), on_off = ifelse(on_off == 0, "OFF", "ON"), ap_q)]
  res3 <- vacaEval[,.(calls = .N, sales = sum(opt_metric), cr = mean(opt_metric)), by = .(date = as.character(date), on_off = ifelse(on_off == 0, "OFF", "ON"), cp_q)]
  
  res1 <- dcast(res1, date ~ on_off , value.var = c("calls", "sales", "cr"))
  res2 <- dcast(res2, date + ap_q ~ on_off , value.var = c("calls", "sales", "cr"))
  res3 <- dcast(res3, date + cp_q ~ on_off , value.var = c("calls", "sales", "cr"))

  res1[, incrementals := (cr_ON - cr_OFF) * calls_ON]
  res2[, incrementals := (cr_ON - cr_OFF) * calls_ON]
  res3[, incrementals := (cr_ON - cr_OFF) * calls_ON]
  
  res2 <- res2[, .(APincrementals = sum(incrementals)), by = date]
  res3 <- res3[, .(CPincrementals = sum(incrementals)), by = date]
  
  res1 <- merge(res1, res2, by = "date")
  res1 <- merge(res1, res3, by = "date")
  
  overall <- res1[, .(date = 'Overall',
                      calls_OFF = sum(calls_OFF),
                      calls_ON = sum(calls_ON),
                      sales_OFF = sum(sales_OFF),
                      sales_ON = sum(sales_ON),
                      incrementals = sum(incrementals),
                      APincrementals = sum(APincrementals),
                      CPincrementals = sum(CPincrementals)
                      )][, `:=`(cr_OFF = sales_OFF/sales_ON,
                                cr_ON = sales_ON/calls_ON)
                      ]
  
  cols <- colnames(res1)
  res2 <- rbindlist(list(res1, overall[, ..cols]))
  res2[, `:=`(ABSGain = incrementals / calls_ON,
              APABSGain = APincrementals / calls_ON,
              CPABSGain = CPincrementals / calls_ON,
              RELGain = 100.0 * (incrementals /(sales_ON - incrementals)),
              APRELGain = 100.0 * (APincrementals /(sales_ON - APincrementals)),
              CPRELGain = 100.0 * (CPincrementals /(sales_ON - CPincrementals))
              
              
              )]
  
  res2 <- round_off(res2)
  
d <- 
kable(res2, 'html') %>%
  kable_styling(bootstrap_options = c("striped", "hover","bordered"), position = "left", full_width = T)
d
}

```


```{r scatter_plot, warning= FALSE , echo= FALSE , message= FALSE}

scatter_plot <- function(opt_metric)
{
   vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)
 
vacaEvalCG <- vacaEval %>%
  inner_join(cg , by = 'callgroup')

curRank <- vacaEvalCG %>%
  group_by(callgroup) %>%
  summarize(calls = n() , CR = mean(optimizationmetric)) %>%
  arrange(CR)
rn_cur <- 1:nrow(curRank)
curRank <- cbind(curRank,rn_cur)

sp1 <- vacaEvalCG %>% 
  group_by(callgroup , rn) %>%
  summarize(calls = n() , CR = mean(optimizationmetric)) %>%
  arrange(CR)
scatterPlot <- sp1 %>%
  left_join(curRank , by = 'callgroup') %>%
  select(callgroup , rn , rn_cur)
correlation <- cor(scatterPlot$rn_cur, scatterPlot$rn)
a <- ggplot(data = scatterPlot , aes(x = rn , y =rn_cur)) +
  geom_point() +
  geom_smooth( method = lm) +
  labs(x = 'Deployed Rank', y = 'Production Rank', title = paste(' Correlation = ', correlation)) #+ 
  # annotate("text", x = 4, y = 20, label = paste(' Correlation = ', correlation))
a
}
```

## Summary Tables
### Gain Summary  {.tabset .tabset-pills}

```{r , results='asis', fig.align= 'center', message=F, warning=F}
optimizations <- colnames(vaca)[grep("optimization",colnames(vaca))]
res <- lapply(optimizations, gain_summary)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  print(res[[optimizations[i]]])
  cat('\n', '<br>', '\n\n')
  
}
```

### CP Stats {.tabset .tabset-pills}

```{r cp_quintile, warning= FALSE , echo= FALSE , message= FALSE, results= 'asis'}

CP_stats <- function(opt_metric){
    vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)
cp_actual_quintile <- vacaEval %>%
  mutate(cp_actual_bucket = floor(cp_actual*params$bucket)) %>%
  group_by(cp_actual_bucket) %>%
  summarize( VA_Delta = (mean(ifelse(ap_actual > params$top , optimizationmetric , NA) ,na.rm = T) - mean(ifelse(ap_actual < (1-params$top) , optimizationmetric , NA) ,na.rm = T))
             , Calls_TopHalf = sum(ifelse(ap_actual > params$top, 1 , NA) ,na.rm = T)
             , Calls_BottomHalf = sum(ifelse(ap_actual < (1-params$top), 1 , NA) ,na.rm = T)
             , APDiff = (mean(ifelse(on_off == '1', ap_actual , NA) ,na.rm = T) - mean(ifelse(on_off == '0', ap_actual , NA) ,na.rm = T))
             , Total_Calls = n()
             , CR = mean(optimizationmetric,na.rm = T)
             , on_AP = mean(ifelse(on_off == '1', ap_actual , NA) ,na.rm = T)
             , off_AP = mean(ifelse(on_off == '0', ap_actual , NA) ,na.rm = T)
             , on_CP = mean(ifelse(on_off == '1', cp_actual , NA) ,na.rm = T)
            , off_CP = mean(ifelse(on_off == '0', cp_actual , NA) ,na.rm = T)
            , OnEvalRaw = mean(ifelse(on_off == "1" , evalscore_raw , NA) , na.rm = T)
            , OffEvalRaw = mean(ifelse(on_off == "0" , evalscore_raw , NA) , na.rm = T)
            , Nagents = mean(nagent, na.rm = T)
             , ABSgain = (mean(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T)) - (mean(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T)))

cp_actual_quintile_off <- vacaEval %>%
  filter(on_off == '0') %>%
  mutate(cp_actual_bucket = floor(cp_actual*params$bucket)) %>%
  group_by(cp_actual_bucket) %>%
  summarize( Off_VA_Delta = (mean(ifelse(ap_actual > params$top , optimizationmetric , NA) ,na.rm = T) - mean(ifelse(ap_actual < (1-params$top) , optimizationmetric , NA) ,na.rm = T))
             , Off_Calls_TopHalf = sum(ifelse(ap_actual > params$top, 1 , NA) ,na.rm = T)
             , Off_Calls_BottomHalf = sum(ifelse(ap_actual < (1-params$top), 1 , NA) ,na.rm = T)
)
  cp_delta <- cp_actual_quintile %>%
    left_join(cp_actual_quintile_off , by = 'cp_actual_bucket') %>%
    select(cp_actual_bucket,VA_Delta,Calls_TopHalf,Calls_BottomHalf,Off_VA_Delta, Off_Calls_TopHalf , Off_Calls_BottomHalf
           ,APDiff, Total_Calls, CR,on_AP,off_AP,on_CP, off_CP,OnEvalRaw, OffEvalRaw, Nagents, ABSgain )

x <- round_off(cp_delta)
# kable(x, 'html') %>% kable_styling(font_size = 12) %>% scroll_box(width = '800px')

d <- kable(x, 'html') %>%
  kable_styling(font_size = 12 , bootstrap_options = c("striped", "hover","bordered"), full_width = T)
d
}


res <- lapply(optimizations, CP_stats)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  print(res[[optimizations[i]]])
  cat('\n', '<br>', '\n\n')
  
}
```

### AP Stats {.tabset .tabset-pills}

```{r ap_quintile, warning= FALSE , echo= FALSE , message= FALSE, results='asis'}

AP_stats <- function(opt_metric){
  
  vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)

ap_actual_quintile <- vacaEval %>%
  mutate(ap_actual_bucket = floor(ap_actual*params$bucket)) %>%
  group_by(ap_actual_bucket) %>%
  dplyr:: summarize( CPDiff = (mean(ifelse(on_off == '1', cp_actual , NA) ,na.rm = T) - mean(ifelse(on_off == '0', cp_actual , NA) ,na.rm = T))
                     , Total_Calls = n()
                     , CR = mean(optimizationmetric,na.rm = T)
                     , on_CP = mean(ifelse(on_off == '1', cp_actual , NA) ,na.rm = T)
                     , off_CP = mean(ifelse(on_off == '0', cp_actual , NA) ,na.rm = T)
                     , on_AP = mean(ifelse(on_off == '1', ap_actual , NA) ,na.rm = T)
                     , off_AP = mean(ifelse(on_off == '0', ap_actual , NA) ,na.rm = T)
                     , OnEvalRaw = mean(ifelse(on_off == "1" , abs(cp_actual - ap_actual) , NA) , na.rm = T)
                     , OffEvalRaw = mean(ifelse(on_off == "0" , abs(cp_actual - ap_actual) , NA) , na.rm = T)
                     , Nagents = mean(nagent, na.rm = T)
                     , ABSgain = (mean(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T)) - (mean(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T)))

x <- round_off(ap_actual_quintile)
# kable(x, 'html') %>% kable_styling(font_size = 12) %>% scroll_box(width = '800px')

d <- kable(x, 'html') %>%
  kable_styling(font_size = 12 , bootstrap_options = c("striped", "hover","bordered"), full_width = T)%>% scroll_box(width = '1200px')
d
}

res <- lapply(optimizations, AP_stats)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  print(res[[optimizations[i]]])
  cat('\n', '<br>', '\n\n')
  
}

```

## Production Stats - Plots
### AP {.tabset .tabset-pills}

```{r AP_Stats, warning= FALSE , echo= FALSE , message= FALSE, results = 'asis'}
AP_stats_plot <- function(opt_metric){
  
  vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)
ap_actual_quintile <- vacaEval %>%
  mutate(ap_bucket = floor(ap_actual*params$bucket)) %>%
  group_by(ap_bucket) %>%
  summarize( on_calls = sum(ifelse(on_off == '1' , 1,0)) , off_call = sum(ifelse(on_off == '0' , 1,0)) , on_CR = mean(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_CR = mean(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T) , on_Sale = sum(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_Sale = sum(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T), incrementals= (on_CR - off_CR)*on_calls , gain = incrementals*100/(on_Sale - incrementals)
  )

ap_loggedinpercentile_quintile <- vacaEval %>%
  mutate(ap_bucket = floor(ap_loggedinpercentile*params$bucket)) %>%
  group_by(ap_bucket) %>%
  summarize( on_calls = sum(ifelse(on_off == '1' , 1,0)) , off_call = sum(ifelse(on_off == '0' , 1,0)) , on_CR_log = mean(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_CR_log = mean(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T) , on_Sale = sum(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_Sale = sum(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T), incrementals= (on_CR_log - off_CR_log)*on_calls , gain = incrementals*100/(on_Sale - incrementals)
)

ap_actual_quintile <- ap_actual_quintile %>%
  left_join(ap_loggedinpercentile_quintile, by = 'ap_bucket') %>%
  select(ap_bucket,on_CR,off_CR, on_CR_log, off_CR_log)


x <- ggplot() +
  ## first plot for on_CR
  geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR, colour = 'On')) +
  geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR, colour = 'On')) +
  # second plot for off_CR
  geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR, colour = 'OFF')) +
  geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR, colour = 'OFF')) +
## third plot for on_CR_log
# geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR_log, colour = 'On_LoggedIn')) +
#   geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR_log, colour = 'On_LoggedIn')) +
  ## fourth plot for off_log
  # geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR_log, colour = 'off_CR_log')) +
  # geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR_log, colour = 'off_CR_log')) +
  scale_color_manual(values = c('red','darkblue')) +
  labs(x = 'Buckets', y = 'CR', title = 'Actual')

a <- (x)

x <- ggplot() +
  ## first plot for on_CR
  # geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR, colour = 'ON_CR')) +
  # geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR, colour = 'ON_CR')) +
  ## second plot for off_CR
  # geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR, colour = 'OFF_Actual')) +
  # geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR, colour = 'OFF_Actual')) +
# third plot for on_CR_log
geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR_log, colour = 'On')) +
  geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=on_CR_log, colour = 'On')) +
# fourth plot for off_log
  geom_point(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR_log, colour = 'Off')) +
  geom_line(data = ap_actual_quintile, aes(x=ap_bucket, y=off_CR_log, colour = 'Off')) +
  scale_color_manual(values = c('red','darkblue')) +
  labs(x = 'Buckets', y = 'CR', title = 'LoggedIn')

b <- (x)
return(list(a = a, b = b))
}

res <- lapply(optimizations, AP_stats_plot)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  plot(res[[optimizations[i]]]$a)
  cat('\n', '<br>', '\n\n')
  
}

```


### AP Loggedin {.tabset .tabset-pills}
``` {r AP_loggedin, warning= FALSE , echo= FALSE , message= FALSE, results = "asis"}

for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  plot(res[[optimizations[i]]]$b)
  cat('\n', '<br>', '\n\n')
  
}

```

### AP Normalised {.tabset .tabset-pills}
``` {r AP_Norm, warning= FALSE , echo= FALSE , message= FALSE, results = "asis"}

AP_norm_plot <- function(opt_metric){
vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)

rpc_per_nf <- vacaEval %>%
  filter(on_off == 0) %>%
  select(nf, optimizationmetric) %>%
  group_by(nf) %>%
  summarise(cr = mean(optimizationmetric)) %>%
  setorder(-cr)

rpc_per_nf_qu <- vacaEval %>%
  select(nf, optimizationmetric, ap_actual) %>%
  mutate(AP_quintile = floor(params$bucket*ap_actual)) %>%
  group_by(AP_quintile, nf) %>%
  filter(!is.na(ap_actual)) %>%
  summarise(cr_qu = mean(optimizationmetric), calls = n())%>%
  setorder(-cr_qu)

j <- merge(rpc_per_nf, rpc_per_nf_qu, by = 'nf')

rpc_per_nf_norm <- j %>%
  filter(cr != 0, calls > 10 )%>%
  mutate(WCR = (cr_qu/abs(cr)) * calls)

rpc_norm <- rpc_per_nf_norm %>%
  group_by(AP_quintile)%>%
  summarise(CR_norm = sum(WCR) * 1.0 / sum(calls), calls_normalised = sum(calls))

x <- ggplot(data = rpc_norm , aes(x = AP_quintile , y = CR_norm)) +
  geom_point() +
  geom_line(color = 'red') +
  labs(x = 'Buckets', y = 'CR_Norm', title = 'Normalized AP on CP decile')

(x)

}

res <- lapply(optimizations, AP_norm_plot)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  plot(res[[optimizations[i]]])
  cat('\n', '<br>', '\n\n')
  
}

```

### CP MA {.tabset .tabset-pills}
```{r CP_Stats, warning= FALSE , echo= FALSE , message= FALSE, results= 'asis'}

CP_stats_plot <- function(opt_metric){
  vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)

  cp_actual_quintile <- vacaEval %>%
    mutate(cp_actual_bucket = floor(cp_actual*params$bucket)) %>%
    group_by(cp_actual_bucket) %>%
    summarize( on_calls = sum(ifelse(on_off == '1' , 1,0)) , off_call = sum(ifelse(on_off == '0' , 1,0)) , on_CR = mean(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_CR = mean(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T) , on_Sale = sum(ifelse(on_off == '1', optimizationmetric , NA) ,na.rm = T) , off_Sale = sum(ifelse(on_off == '0', optimizationmetric , NA) ,na.rm = T), incrementals= (on_CR - off_CR)*on_calls , gain = incrementals*100/(on_Sale - incrementals)
    )
  x <- round_off(cp_actual_quintile)
  x <- ggplot() +
    ## first plot for on
    geom_point(data = cp_actual_quintile, aes(x=cp_actual_bucket, y=on_CR, colour = 'ON')) +
    geom_line(data = cp_actual_quintile, aes(x=cp_actual_bucket, y=on_CR, colour = 'ON')) +
    ## Second plot for off
    geom_point(data = cp_actual_quintile, aes(x=cp_actual_bucket, y=off_CR, colour = 'OFF')) +
    geom_line(data = cp_actual_quintile, aes(x=cp_actual_bucket, y=off_CR, colour = 'OFF')) +
    scale_color_manual(values = c('red','darkblue')) +
    labs(x = 'Buckets', y = 'CR', title = 'CR')
  
  a <- (x)
  
  cp_actual_quintile_off <- vacaEval %>%
    filter(on_off == '0') %>%
    mutate(cp_actual_bucket = floor(cp_actual*params$bucket)) %>%
    group_by(cp_actual_bucket) %>%
    summarize( Off_VA_Delta = (mean(ifelse(ap_actual > params$top , optimizationmetric , NA) ,na.rm = T) - mean(ifelse(ap_actual < (1-params$top) , optimizationmetric , NA) ,na.rm = T))
               , Off_Calls_TopHalf = sum(ifelse(ap_actual > params$top, 1 , NA) ,na.rm = T)
               , Off_Calls_BottomHalf = sum(ifelse(ap_actual < (1-params$top), 1 , NA) ,na.rm = T)
  )
    cp_delta <- cp_actual_quintile %>%
      left_join(cp_actual_quintile_off , by = 'cp_actual_bucket') %>%
      select(cp_actual_bucket,Off_VA_Delta, Off_Calls_TopHalf , Off_Calls_BottomHalf )
  
  cp_delta <- round_off(cp_delta)
  
  
  x <- ggplot() +
    ## first plot for on
    geom_point(data = cp_delta, aes(x=cp_actual_bucket, y=Off_VA_Delta, colour = 'Off_VA')) +
    geom_line(data = cp_delta, aes(x=cp_actual_bucket, y=Off_VA_Delta, colour = 'Off_VA')) +
    scale_color_manual(values = c('darkgreen')) +
    labs(x = 'Buckets', y = 'CR', title = ' Delta ')
  
  b <- (x)
  return(list(a = a, b = b))
}

res <- lapply(optimizations, CP_stats_plot)
names(res) <- optimizations
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  print(res[[optimizations[i]]]$a)
  cat('\n', '<br>', '\n\n')
  
}
```

### CP VA {.tabset .tabset-pills}
```{r CP_Stats_2, warning= FALSE , echo= FALSE , message= FALSE, results= 'asis'}
for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  print(res[[optimizations[i]]]$b)
  cat('\n', '<br>', '\n\n')
  
}

```



## Gain by DiffGroup
```{r gainByEval, warning= FALSE , echo= FALSE , message= FALSE, include = FALSE}

gainbydg <- function(opt_metric){
  vacaEval <- vacaEval %>% mutate_(optimizationmetric = opt_metric)

gainbyeval <- data.frame(evalscore = vacaEval$evalscore_raw,
                         cq = floor(vacaEval$cp_actual * params$bucket),
                         aq = floor(vacaEval$ap_actual * params$bucket),
                         opt = vacaEval$optimizationmetric,
                         on_off = vacaEval$on_off,
                         evalint = floor(vacaEval$evalscore_raw * 100))


agentquality <- gainbyeval%>%filter(on_off == 0) %>% group_by(aq) %>% summarise(AgentQuality = mean(opt))
callerquality <- gainbyeval%>%filter(on_off == 0)  %>% group_by(cq) %>% summarise(CallerQuality = mean(opt))

gainbyeval1 <- merge(x=gainbyeval , y=agentquality ,by.x = "aq", by.y = "aq" )
gainbyeval2 <- merge(x=gainbyeval1 , y=callerquality , by.x = "cq" , by.y = "cq") #At this point you have agent and call quality on each call
gainbyevaloff <- gainbyeval2 %>% filter(on_off == 0)

dg <- max(gainbyeval2$evalint)             #Max Diffgroup
basecr = mean(gainbyeval2$opt)            #on+offCR at Max DG
baseaq = mean(gainbyeval2$AgentQuality)   #on+off AgentQuality at Max DG
basecq = mean(gainbyeval2$CallerQuality)  #on+off Callquality at Max DG
baseoffcalls = sum(as.integer(!gainbyeval2$on_off)) #Off Calls at Max DG
baseoncalls = sum(gainbyeval2$on_off)     #On calls at Max DG

dgoff <- max(gainbyevaloff$evalint)             #Max Diffgroup
basecroff = mean(gainbyevaloff$opt)            #offCR at Max DG
baseaqoff = mean(gainbyevaloff$AgentQuality)   #off AgentQuality at Max DG
basecqoff = mean(gainbyevaloff$CallerQuality)  #off Callquality at Max DG

gainbydg <- data.frame(
  diffgroup = dg ,CR = basecr, unadjgain =  0 ,apcorrection = 0 ,cpcorrection =0, adjustedgain=0 , On=1 , Off=1
)
gainbydgoff <- data.frame(
  diffgroup = dgoff ,CR = basecroff, unadjgain =  0 ,apcorrection = 0 ,cpcorrection =0, adjustedgain=0
)

for(i in 1:dg){
  dgtemp <- dg - i

  temp <- gainbyeval2 %>% filter(evalint <= dgtemp ) %>% summarise(diffgroup = max(evalint),CR = mean(opt),
                                                                   unadjgain = (mean(opt)-basecr)
                                                                   , apcorrection = (mean(AgentQuality)-baseaq), cpcorrection = (mean(CallerQuality)-basecq),
                                                                   adjustedgain = (mean(opt)-basecr) - (mean(AgentQuality)-baseaq)  - (mean(CallerQuality)-basecq)
                                                                   , On = sum(on_off)/baseoncalls, Off = sum(as.integer(!on_off))/baseoffcalls
  )

  tempoff <- gainbyevaloff %>% filter(evalint <= dgtemp) %>% summarise(diffgroup = max(evalint),CR = mean(opt),unadjgain = (mean(opt)-basecroff)
                                                                       , apcorrection = (mean(AgentQuality)-baseaqoff) , cpcorrection = (mean(CallerQuality)-basecqoff),
                                                                       adjustedgain = (mean(opt)-basecroff) - (mean(AgentQuality)-baseaqoff) - (mean(CallerQuality)-basecqoff)
  )

  gainbydg <- rbind(gainbydg , temp)
  gainbydgoff <- rbind(gainbydgoff , tempoff)

  temp <- data.frame();
  tempoff <- data.frame();
}
x <- ggplot(gainbydg, aes(x = diffgroup)) +
  geom_line(aes(y = apcorrection, colour ="apcorrection")) +
  geom_line(aes(y = cpcorrection, colour = "cpcorrection"))+
  geom_line(aes(y = unadjgain, colour = "unadjgain"))+
  geom_line(aes(y = adjustedgain, colour = "adjustedgain"))+
  scale_color_manual(values=c("orange" , "#7faef9", "black" , "green"))+
  ylab( "Gain")+
  labs(colour = "legend")+
  ggtitle("On + Off")

y <- ggplot(gainbydgoff, aes(x = diffgroup)) +
  geom_line(aes(y = apcorrection, colour ="apcorrection")) +
  geom_line(aes(y = cpcorrection, colour = "cpcorrection"))+
  geom_line(aes(y = unadjgain, colour = "unadjgain"))+
  geom_line(aes(y = adjustedgain, colour = "adjustedgain"))+
  scale_color_manual(values=c("orange" , "#7faef9", "black" , "green"))+
  ylab( "Gain")+
  labs(colour = "legend")+
  ggtitle("Off")

 return(list(a = x, b = y))
}

res <- lapply(optimizations, gainbydg)
names(res) <- optimizations

```

### Gain by Diffgroup ON+OFF {.tabset .tabset-pills}
```{r plotGainByEval_1, warning= FALSE , echo= FALSE , message= FALSE, results = "asis"}

for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  plot(res[[optimizations[i]]]$a)
  cat('\n', '<br>', '\n\n')
  
}

```

### Gain by Diffgroup OFF {.tabset .tabset-pills}
```{r plotGainByEval_2, warning= FALSE , echo= FALSE , message= FALSE, results = "asis"}

for(i in 1:length(res)) {
  cat("####", params$optimizationmetric[i], '<br>', '\n')
  plot(res[[optimizations[i]]]$b)
  cat('\n', '<br>', '\n\n')
  
}

```
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
